Data summary and analysis procedure: dual RNA-seq of \textit{Eimeria falciformis} infected \textit{Mus musculus}

### 2016-08-07 figuresANDmanuscript/manuscriptBMCformat/manuscript_rnaseq.tex
Before moving to feature counts and implementing the normalization correctly

%%% Load packages
%\usepackage{amsthm,amsmath}
%\RequirePackage{natbib}
%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
%\RequirePackage{hyperref}
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
%\usepackage{siunitx}
\usepackage[colorlinks]{hyperref} % To color blocks of text 
%\usepackage[dvipsnames]{xcolor} % More color options (see Wikibooks)  
\usepackage{changepage}
\usepackage{booktabs} % For prettier tables
\usepackage{float} % To control positions of e.g. tables or figures
%\usepackage[section]{placeins}
\usepackage{graphicx}
\graphicspath{ {../} }

@@

The number of sequencing reads obtained for individual replicates
ranged from 21,517,055 (sample NMRI\_sporozoites\_rep2) to 593,396,312
(NMRI\_2ndInf\_5dpi\_rep1).

@@

>>>>

%%% Load packages
%\usepackage{amsthm,amsmath}
%\RequirePackage{natbib}
%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
%\RequirePackage{hyperref}
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
%\usepackage{siunitx}
\usepackage[colorlinks]{hyperref} % To color blocks of text 
%\usepackage[dvipsnames]{xcolor} % More color options (see Wikibooks)  
\usepackage{changepage}
\usepackage{booktabs} % For prettier tables
\usepackage{float} % To control positions of e.g. tables or figures
%\usepackage[section]{placeins}
\usepackage{graphicx}

% to color table rows
\usepackage{color, colortbl}
\graphicspath{ {../} }

@@

The number of sequence read mappings obtained for individual
replicates ranged from 21,517,055 (sample NMRI\_sporozoites\_rep2) to
593,396,312 (NMRI\_2ndInf\_5dpi\_rep1).

@@

\newcommand{\bcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{LightRed}{rgb}{1,0.88,1}

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Fri Aug  5 13:00:01 2016
\begin{table}[ht]
\caption{Experimental design, sequencing output and mapping statistics.}
\centering
\hspace*{-1.5cm}\begin{tabular}{lllllllll}
  \hline
Sample & \bcell{Sequencing\\method} & batch & \bcell{read mappings\\Mouse} & \bcell{read mappings\\\textit{E. falciformis}} & \bcell{Percentage\\\textit{E. falciformis}} & dpi & infection  \\ 
\hline
  NMRI\_2ndInf\_0dpi\_rep1 & GAII & 2 & 285032128 & 326 & 0 & 0dpi & Challenge \\ 
  Rag\_0dpi\_rep1 & hiseq & 3 & 43414004 & 474 & 0.001 & 0dpi & None \\ 
  C57BL6\_0dpi\_rep1 & hiseq & 3 & 53877840 & 491 & 0.001 & 0dpi & None \\ 
  C57BL6\_0dpi\_rep2 & hiseq & 3 & 76753491 & 657 & 0.001 & 0dpi & None \\ 
  Rag\_0dpi\_rep2 & hiseq & 3 & 80702547 & 730 & 0.001 & 0dpi & None \\ 
  NMRI\_2ndInf\_0dpi\_rep2 & hiseq & 3 & 90681785 & 3738 & 0.004 & 0dpi & Challenge \\ 
  \rowcolor{LightCyan}
  NMRI\_2ndInf\_3dpi\_rep1 & hiseq & 3 & 91352242 & 5355 & 0.006 & 3dpi & Challenge \\ 
  \rowcolor{LightCyan}
  NMRI\_2ndInf\_5dpi\_rep2 & hiseq & 3 & 113957667 & 12692 & 0.011 & 5dpi & Challenge \\ 
  \rowcolor{LightRed}
  NMRI\_1stInf\_0dpi\_rep1 & GAII & 1 & 229165002 & 31459 & 0.014 & 0dpi & None \\ 
  NMRI\_2ndInf\_3dpi\_rep2 & hiseq & 3 & 106446839 & 34699 & 0.033 & 3dpi & Challenge \\ 
  NMRI\_2ndInf\_7dpi\_rep2 & hiseq & 3 & 122999109 & 46700 & 0.038 & 7dpi & Challenge \\ 
  Rag\_1stInf\_5dpi\_rep1 & hiseq & 3 & 71173382 & 73445 & 0.103 & 5dpi & First \\ 
  Rag\_1stInf\_5dpi\_rep2 & hiseq & 3 & 57192380 & 113673 & 0.198 & 5dpi & First \\ 
  C57BL6\_1stInf\_5dpi\_rep1 & hiseq & 3 & 65523435 & 217606 & 0.331 & 5dpi & First \\ 
  Rag\_2ndInf\_5dpi\_rep1 & hiseq & 3 & 85288323 & 224273 & 0.262 & 5dpi & Challenge \\ 
  C57BL6\_1stInf\_5dpi\_rep2 & hiseq & 3 & 32887009 & 250954 & 0.757 & 5dpi & First \\ 
  C57BL6\_2ndInf\_5dpi\_rep1 & hiseq & 3 & 62053975 & 311900 & 0.500 & 5dpi & Challenge \\ 
  NMRI\_1stInf\_3dpi\_rep1 & GAII & 1 & 209723287 & 815820 & 0.388 & 3dpi & First \\ 
  NMRI\_1stInf\_3dpi\_rep2 & GAII & 2 & 515516785 & 903330 & 0.175 & 3dpi & First \\ 
  NMRI\_1stInf\_5dpi\_rep2 & GAII & 2 & 316721928 & 1609009 & 0.505 & 5dpi & Firs \\ 
  NMRI\_2ndInf\_5dpi\_rep1 & GAII & 2 & 589643389 & 3752923 & 0.632 & 5dpi & Challenge \\ 
  NMRI\_2ndInf\_7dpi\_rep1 & hiseq & 3 & 97221189 & 9927803 & 9.265 & 7dpi & Challenge \\ 
  NMRI\_1stInf\_5dpi\_rep1 & GAII & 2 & 204647381 & 18549727 & 8.311 & 5dpi & First \\ 
  NMRI\_sporozoites\_rep2 & GAII & 0 & 8702 & 21508353 & 99.960 & \textit{in vitro} & \textit{in vitro} \\ 
  NMRI\_1stInf\_5dpi\_rep3 & GAII & 0 & 334671421 & 54022504 & 13.899 & 5dpi & First \\ 
  NMRI\_1stInf\_7dpi\_rep1 & GAII & 1 & 12532238 & 79648900 & 86.405 & 7dpi & First \\ 
  NMRI\_sporozoites\_rep1 & GAII & 1 & 13800 & 92259539 & 99.985 & \textit{in vitro} & \textit{in vitro} \\ 
  NMRI\_oocysts\_rep1 & GAII & 1 & 11676 & 108477484 & 99.989 & envir. & envir. \\ 
  NMRI\_oocysts\_rep2 & GAII & 0 & 19024 & 126543533 & 99.985 & envir. & envir. \\ 
  NMRI\_1stInf\_7dpi\_rep2 & GAII & 1 & 94310278 & 154343046 & 62.072 & 7dpi & First \\ 
   \hline
\hspace*{+1.5cm}\end{tabular}
\begin{tablenotes}
  \small
\item *envir. ``environmental'' oocysts sporulated in potassium dichromate. \\
\item *\textit{in vitro} in vitro sporulated oocysts
\end{tablenotes}
\end{table}

### 2016-08-07 figuresANDmanuscript/table_rc.tex
Before moving to feature counts and implementing the normalization correctly

% latex table generated in R 3.3.0 by xtable 1.8-2 package
% Wed Jun 22 17:40:30 2016
\begin{table}[ht]
\centering
\begin{tabular}{lllll}
  \hline
Sample & Mouse transcripts & E. falciformis transcripts & Percentage E. falciformis & \#E. falciformis genes \\ 
  \hline
NMRI\_oocysts\_rep1 & 11676.000 & 108477484.000 & 99.989 & 5734.000 \\ 
  NMRI\_oocysts\_rep2 & 19024.000 & 126543533.000 & 99.985 & 5774.000 \\ 
  NMRI\_sporozoites\_rep1 & 13800.000 & 92259539.000 & 99.985 & 5808.000 \\ 
  NMRI\_sporozoites\_rep2 & 8702.000 & 21508353.000 & 99.960 & 5564.000 \\ 
  NMRI\_1stInf\_7dpi\_rep1 & 12532238.000 & 79648900.000 & 86.405 & 5894.000 \\ 
  NMRI\_1stInf\_7dpi\_rep2 & 94310278.000 & 154343046.000 & 62.072 & 5897.000 \\ 
  NMRI\_1stInf\_5dpi\_rep3 & 334671421.000 & 54022504.000 & 13.899 & 5794.000 \\ 
  NMRI\_2ndInf\_7dpi\_rep1 & 97221189.000 & 9927803.000 & 9.265 & 5865.000 \\ 
  NMRI\_1stInf\_5dpi\_rep1 & 204647381.000 & 18549727.000 & 8.311 & 5739.000 \\ 
  C57BL6\_1stInf\_5dpi\_rep2 & 32887009.000 & 250954.000 & 0.757 & 3946.000 \\ 
  NMRI\_2ndInf\_5dpi\_rep1 & 589643389.000 & 3752923.000 & 0.632 & 5602.000 \\ 
  NMRI\_1stInf\_5dpi\_rep2 & 316721928.000 & 1609009.000 & 0.505 & 5439.000 \\ 
  C57BL6\_2ndInf\_5dpi\_rep1 & 62053975.000 & 311900.000 & 0.500 & 4610.000 \\ 
  NMRI\_1stInf\_3dpi\_rep1 & 209723287.000 & 815820.000 & 0.388 & 5466.000 \\ 
  C57BL6\_1stInf\_5dpi\_rep1 & 65523435.000 & 217606.000 & 0.331 & 4259.000 \\ 
  Rag\_2ndInf\_5dpi\_rep1 & 85288323.000 & 224273.000 & 0.262 & 4251.000 \\ 
  Rag\_1stInf\_5dpi\_rep2 & 57192380.000 & 113673.000 & 0.198 & 2969.000 \\ 
  NMRI\_1stInf\_3dpi\_rep2 & 515516785.000 & 903330.000 & 0.175 & 5101.000 \\ 
  Rag\_1stInf\_5dpi\_rep1 & 71173382.000 & 73445.000 & 0.103 & 2748.000 \\ 
  NMRI\_2ndInf\_7dpi\_rep2 & 122999109.000 & 46700.000 & 0.038 & 2174.000 \\ 
  NMRI\_2ndInf\_3dpi\_rep2 & 106446839.000 & 34699.000 & 0.033 & 1901.000 \\ 
  NMRI\_1stInf\_0dpi\_rep1 & 229165002.000 & 31459.000 & 0.014 & 1380.000 \\ 
  NMRI\_2ndInf\_5dpi\_rep2 & 113957667.000 & 12692.000 & 0.011 & 539.000 \\ 
  NMRI\_2ndInf\_3dpi\_rep1 & 91352242.000 & 5355.000 & 0.006 & 121.000 \\ 
  NMRI\_2ndInf\_0dpi\_rep2 & 90681785.000 & 3738.000 & 0.004 & 62.000 \\ 
  Rag\_0dpi\_rep1 & 43414004.000 & 474.000 & 0.001 & 2.000 \\ 
  C57BL6\_0dpi\_rep1 & 53877840.000 & 491.000 & 0.001 & 2.000 \\ 
  C57BL6\_0dpi\_rep2 & 76753491.000 & 657.000 & 0.001 & 2.000 \\ 
  Rag\_0dpi\_rep2 & 80702547.000 & 730.000 & 0.001 & 3.000 \\ 
  NMRI\_2ndInf\_0dpi\_rep1 & 285032128.000 & 326.000 & 0.000 & 2.000 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Fri Aug  5 13:00:01 2016
\begin{table}[ht]
\centering
\begin{tabular}{lllllllll}
  \hline
Sample & Sequencing method & batch & read mappings Mouse & read mappings E. falciformis & Percentage E. falciformis & dpi & challenged & \# E. falciformis genes \\ 
  \hline
NMRI\_2ndInf\_0dpi\_rep1 & GAII & 2 & 285032128.000 & 326.000 & 0.000 & 0dpi & Callenge & 2.000 \\ 
  Rag\_0dpi\_rep1 & hiseq & 3 & 43414004.000 & 474.000 & 0.001 & 0dpi & None & 2.000 \\ 
  C57BL6\_0dpi\_rep1 & hiseq & 3 & 53877840.000 & 491.000 & 0.001 & 0dpi & None & 2.000 \\ 
  C57BL6\_0dpi\_rep2 & hiseq & 3 & 76753491.000 & 657.000 & 0.001 & 0dpi & None & 2.000 \\ 
  Rag\_0dpi\_rep2 & hiseq & 3 & 80702547.000 & 730.000 & 0.001 & 0dpi & None & 3.000 \\ 
  NMRI\_2ndInf\_0dpi\_rep2 & hiseq & 3 & 90681785.000 & 3738.000 & 0.004 & 0dpi & Callenge & 62.000 \\ 
  NMRI\_2ndInf\_3dpi\_rep1 & hiseq & 3 & 91352242.000 & 5355.000 & 0.006 & 3dpi & Callenge & 121.000 \\ 
  NMRI\_2ndInf\_5dpi\_rep2 & hiseq & 3 & 113957667.000 & 12692.000 & 0.011 & 5dpi & Callenge & 539.000 \\ 
  NMRI\_1stInf\_0dpi\_rep1 & GAII & 1 & 229165002.000 & 31459.000 & 0.014 & 0dpi & None & 1380.000 \\ 
  NMRI\_2ndInf\_3dpi\_rep2 & hiseq & 3 & 106446839.000 & 34699.000 & 0.033 & 3dpi & Callenge & 1901.000 \\ 
  NMRI\_2ndInf\_7dpi\_rep2 & hiseq & 3 & 122999109.000 & 46700.000 & 0.038 & 7dpi & Callenge & 2174.000 \\ 
  Rag\_1stInf\_5dpi\_rep1 & hiseq & 3 & 71173382.000 & 73445.000 & 0.103 & 5dpi & First & 2748.000 \\ 
  Rag\_1stInf\_5dpi\_rep2 & hiseq & 3 & 57192380.000 & 113673.000 & 0.198 & 5dpi & First & 2969.000 \\ 
  C57BL6\_1stInf\_5dpi\_rep1 & hiseq & 3 & 65523435.000 & 217606.000 & 0.331 & 5dpi & First & 4259.000 \\ 
  Rag\_2ndInf\_5dpi\_rep1 & hiseq & 3 & 85288323.000 & 224273.000 & 0.262 & 5dpi & Callenge & 4251.000 \\ 
  C57BL6\_1stInf\_5dpi\_rep2 & hiseq & 3 & 32887009.000 & 250954.000 & 0.757 & 5dpi & First & 3946.000 \\ 
  C57BL6\_2ndInf\_5dpi\_rep1 & hiseq & 3 & 62053975.000 & 311900.000 & 0.500 & 5dpi & Callenge & 4610.000 \\ 
  NMRI\_1stInf\_3dpi\_rep1 & GAII & 1 & 209723287.000 & 815820.000 & 0.388 & 3dpi & First & 5466.000 \\ 
  NMRI\_1stInf\_3dpi\_rep2 & GAII & 2 & 515516785.000 & 903330.000 & 0.175 & 3dpi & First & 5101.000 \\ 
  NMRI\_1stInf\_5dpi\_rep2 & GAII & 2 & 316721928.000 & 1609009.000 & 0.505 & 5dpi & First & 5439.000 \\ 
  NMRI\_2ndInf\_5dpi\_rep1 & GAII & 2 & 589643389.000 & 3752923.000 & 0.632 & 5dpi & Callenge & 5602.000 \\ 
  NMRI\_2ndInf\_7dpi\_rep1 & hiseq & 3 & 97221189.000 & 9927803.000 & 9.265 & 7dpi & Callenge & 5865.000 \\ 
  NMRI\_1stInf\_5dpi\_rep1 & GAII & 2 & 204647381.000 & 18549727.000 & 8.311 & 5dpi & First & 5739.000 \\ 
  NMRI\_sporozoites\_rep2 & GAII & 0 & 8702.000 & 21508353.000 & 99.960 & environmental & environmental & 5564.000 \\ 
  NMRI\_1stInf\_5dpi\_rep3 & GAII & 0 & 334671421.000 & 54022504.000 & 13.899 & 5dpi & First & 5794.000 \\ 
  NMRI\_1stInf\_7dpi\_rep1 & GAII & 1 & 12532238.000 & 79648900.000 & 86.405 & 7dpi & First & 5894.000 \\ 
  NMRI\_sporozoites\_rep1 & GAII & 1 & 13800.000 & 92259539.000 & 99.985 & environmental & environmental & 5808.000 \\ 
  NMRI\_oocysts\_rep1 & GAII & 1 & 11676.000 & 108477484.000 & 99.989 & environmental & environmental & 5734.000 \\ 
  NMRI\_oocysts\_rep2 & GAII & 0 & 19024.000 & 126543533.000 & 99.985 & environmental & environmental & 5774.000 \\ 
  NMRI\_1stInf\_7dpi\_rep2 & GAII & 1 & 94310278.000 & 154343046.000 & 62.072 & 7dpi & First & 5897.000 \\ 
   \hline
\end{tabular}
\end{table}
